The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
use template docx
fix text refs space :

output: 
    # bookdown::word_document2
    github_document

@@

(ref:lcres) : varying scale in landcover resolution. For each landcover resolution (10m, 100m, 250m, 500m and 1000m), ultilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m. Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution. B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution. C) Mean layer relevance and D) mean graph strength across individuals showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.

@@

(ref:socres) : varying scale in social threshold. For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers. B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau around 0.65 before decrease between 400m and 500m. C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers remained consistently sparse.

@@

(ref:winlen) : varying scale in time window length. For each time windown length (of a sequence from 40 to 100 by 5), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau around 0.65 before decrease between 400m and 500m. C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers remained consistently sparse.

@@

(ref:nobs) : varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete dataset to construct multilayer networks with layers defined by each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open. B) Mean connective redundancy across individuals increased with increasing number of observations, with a decreasing rate of increase around 100 observations. C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers. D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained sparse throughout for summer layers.

@@

(ref:winpos) : varying scale in time window position. For each time windown position (of a sequence from 1 to 48), the time window used to define seasons was shifted and multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers. C) Mean layer relevance decreased for winter layers and increased for summer layers, showing greater connectivity in summer layers at later window positions. D) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.

>>>>

output: 
    bookdown::word_document2:
      reference_docx: template.docx
    # github_document

@@

(ref:lcres): varying scale in landcover resolution. For each landcover resolution (10m, 100m, 250m, 500m and 1000m), ultilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m. Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution. B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution. C) Mean layer relevance and D) mean graph strength across individuals showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.

@@

(ref:socres): varying scale in social threshold. For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers. B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau around 0.65 before decrease between 400m and 500m. C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers remained consistently sparse.

@@

(ref:winlen): varying scale in time window length. For each time windown length (of a sequence from 40 to 100 by 5), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau around 0.65 before decrease between 400m and 500m. C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers remained consistently sparse.

@@

(ref:nobs): varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete dataset to construct multilayer networks with layers defined by each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open. B) Mean connective redundancy across individuals increased with increasing number of observations, with a decreasing rate of increase around 100 observations. C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers. D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained sparse throughout for summer layers.

@@

(ref:winpos): varying scale in time window position. For each time windown position (of a sequence from 1 to 48), the time window used to define seasons was shifted and multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers. C) Mean layer relevance decreased for winter layers and increased for summer layers, showing greater connectivity in summer layers at later window positions. D) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
